Misperceived Social Norms about Women Working Outside the Home and Its Effect on Women in Saudi Arabia

### 2024-02-13 outputs/paper/paper.qmd
Change Table 1 result description

By using the regression analysis, we examine the treatment effect on the participants' likelihood to sign up for a job matching service for their wives. The treatment variable is significant across all model specifications, with coefficients ranging from 0.0853 to 0.0899. The constant term varies considerably across different model specifications, suggesting differing baseline propensities for signing up absent the treatment. The p-values for the treatment effect, under various robustness checks such as robust standard errors, wild bootstrap, and permutation test, all indicate significance, ranging from 0.008 to 0.038. These results reinforcing the treatment's positive impact on sign-up rates (@tbl-summary_table).

@@

Another study @OrganizedDiffusio has evaluated the impact of "organized diffusion" on community-based health and women's empowerment programs. This approach involves encouraging individuals who have received training or information to share it with others, thus spreading the benefits more widely. The study, which looked at programs in Mali, Nepal, and Nigeria, found that implementing this method can lead to significant changes in social norms without incurring additional costs.

>>>>

@tbl-summary_table presents the successful randomization in the experiment, which is evident from the comparable statistics between the treatment and control groups. For instance, both groups have almost identical average age, with the control group at 24.64 years and the treatment group at 24.91 years. Similarly, the employment rates are also similar, with 87.45% employed in the control group as compared to 85.77% in the treatment group. Additionally, the percentage of participants with a college degree is also balanced, with 55.06% in the control group and 57.31% in the treatment group. These figures imply that any differences in the intervention outcomes can be confidently attributed to the treatment itself rather than to underlying demographic differences.

@@

Another study @OrganizedDiffusion has evaluated the impact of "organized diffusion" on community-based health and women's empowerment programs. This approach involves encouraging individuals who have received training or information to share it with others, thus spreading the benefits more widely. The study, which looked at programs in Mali, Nepal, and Nigeria, found that implementing this method can lead to significant changes in social norms without incurring additional costs.
